### 2016-09-27 notions.tex
small changes

In this experiment we track the time complexity (relative to some
model of computation) and query complexity (i.e., number of
queries to $\TestOracle$) of~$A$.
We define the advantage of adversary~$A$ in the correctness experiment as
$\AdvCorrect{\Pi,r}{A} = \Prob{\ExpCorrect{\Pi,r}{A}=1}$.
Overloading notation, we write $\AdvCorrect{\Pi,r}{t,q}$ for the maximum over
all~$t$-time adversaries that ask at most~$q$ queries. We say a
data structure~$\Pi$ is $(t,q,r,\epsilon)$-correct if $\AdvCorrect{\Pi,r}{t,q} \leq \epsilon$.

@@

\begin{figure}[hbtp]
\centering
\fpage{.6}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpPrivSSreal{\Pi}{A}$}\\
$S \getsr A$ \\
$(\pubaux,\privaux) \getsr \Rep(S)$\\
return $A(\pubaux)$\\
}
%
{
\experimentv{$\ExpPrivSSsim{\Pi, {\sf leak}}{A, \Sim}$}\\
$S \getsr A$\\
$\pubaux \getsr \Sim({\sf leak}(S))$ \\
return $A(\pubaux)$\\
}
}
\caption{Experiments for a ``semantic-security'' style privacy
  definition.}
\label{fig:privacy-ss}
\end{figure}

>>>>

In this experiment we track the time complexity (relative to some
model of computation) and query complexity (i.e., number of
queries to $\TestOracle$) of~$A$.
We define the advantage of adversary~$A$ in the correctness experiment as
$\AdvCorrect{\Pi,r}{A} = \Prob{\ExpCorrect{\Pi,r}{A}=1}$.
\tsnote{drop} Overloading notation, we write $\AdvCorrect{\Pi,r}{t,q}$ for the maximum over
all~$t$-time adversaries that ask at most~$q$ queries. We say a
data structure~$\Pi$ is $(t,q,r,\epsilon)$-correct if $\AdvCorrect{\Pi,r}{t,q} \leq \epsilon$.

@@

\begin{figure}[hbtp]
\centering
\fpage{.6}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpPrivSSreal{\Pi}{A}$}\\
$S \getsr A$ \\
$(\pubaux,\privaux) \getsr \Rep(S)$\\
return $A(\pubaux)$\\
}
%
{
\experimentv{$\ExpPrivSSsim{\Pi, {\sf leak}}{A, \Sim}$}\\
$S \getsr A$\\
$\pubaux \getsr \Sim({\sf leak}(S))$ \\
return $A(\pubaux)$\\
}
}
\caption{Experiments for the ``semantic-security'' privacy
  definition.}
\label{fig:privacy-ss}

\end{figure}
\begin{figure}[hbtp]
\centering
\fpage{.6}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpPrivSSreal{\Pi,\distr{}{}}{A}$}\\
$S \getsr \distr{}{}$ \\
$(\pubaux,\privaux) \getsr \Rep(S)$\\
return $A(S,\pubaux)$\\
}
%
{
\experimentv{$\ExpPrivSSsim{\Pi, {\sf leak}, \distr{}{}}{A, \Sim}$}\\
$S \getsr \distr{}{}$\\
$\pubaux \getsr \Sim({\sf leak}(S))$ \\
return $A(S,\pubaux)$\\
}
}
\caption{Experiments for the ``distibutional semantic-security'' privacy
  definition.}
\label{fig:privacy-dss}
\end{figure}
